```{r ReadTrimIncome ANCOVA by R file, echo = F, warning = F}
source(paste0(pathprogram, "ReadTrimIncomeANCOVA.R"))
```
Income sources are mainly labour incomes (`lab`) and farm revenues (`far`) with `r nrow(lab[o800 == 1L & tee == 2,])` and `r nrow(far[o800 == 1L & tee == 2,])` observations at baseline, respectively. We ignore farm incomes due to small number of observations.

<details><summary>Click here to see the code of labour income impacts estimation.</summary>
```{r Labour income regression set parameters original HHs}
source(paste0(pathprogram, "ReadTrimIncomeANCOVA.R"))
FileName <- "LabourIncome"
#### Regression types
FileNameHeader <- c("", "PovertyStatus", "Attributes",
  "TimeVarying", "TimeVaryingAttributes",
  "TimeVaryingPovertyStatus", "TimeVaryingPovertyStatusAttributes")
regsuffixes <- c("", "a", "P", "T", "Ta", "TP", "TPa")
listheader <- paste0("lb", regsuffixes)
exclheader <- paste0("excl", regsuffixes)
inclheader <- gsub("ex", "in", exclheader)
#### Regression specifications: Selecting covariates
source(paste0(pathprogram, "LabourIncomeCovariateSelectionANCOVA3.R"))
#### Number of regression specifications = jay
jay <- max(as.numeric(gsub("incl", "", ls(pattern = "^incl\\d"))))
Regressands <- c(rep("TotalHHLabourIncome", 6))
DataToUse1 <- DataToUse2 <- rep("lab", 6)
Addseparatingcols = NULL; Separatingcolwidth = NULL
Separatingcoltitle = NULL
#### Use livestock data to attach NumCows0, HadCows, livestock values
source(paste0(pathprogram, "ReadTrimIncomeANCOVA.R"))
dig.depmean <- 0
AddMeanStdColumn <- UseRawDataForDestat <- T
source(paste0(pathprogram, "ANCOVAEstimationFile3.R"))
```
</details>
```{r Farm income regression set parameters original HHs, echo = F}
FileName <- "FarmIncome"
FileNameHeader <- c("", "Attributes", "PovertyStatus", 
  "TimeVarying", "TimeVaryingAttributes")
regsuffixes <- c("", "a", "P", "T", "Ta")
listheader <- paste0("fr", regsuffixes)
exclheader <- paste0("excl", regsuffixes)
inclheader <- gsub("ex", "in", exclheader)
source(paste0(pathprogram, "FarmIncomeCovariateSelectionANCOVA2.R"))
jay <- max(as.numeric(gsub("incl", "", ls(pattern = "^incl\\d"))))
Regressands <- rep("TotalRevenue", 3)
DataToUse1 <- DataToUse2 <- rep("far", 3)
Addseparatingcols = NULL; Separatingcolwidth = NULL
Separatingcoltitle = NULL
dig.depmean <- 0
AddMeanStdColumn <- UseRawDataForDestat <- T
source(paste0(pathprogram, "ANCOVAEstimationFile3.R"))
```

<details><summary>Click here to see the table of time varying labour income impacts by arm.</summary>
`r HTML_LabourIncomeTimeVarying`
</details>
