```{r ReadTrimConsumption OLS, echo = F, cache = F, warning = F}
source(paste0(pathprogram, "ReadTrimConsumptionANCOVA.R"))
```

Consumption is observed in rd 2-4. There are `r nrow(con)` observations. As we lack the initial value, we use OLS using rd 2- 4 values to measure the impacts. It should be less precise but still gives consistent estimates.  

6 regression specifications differ in terms of regressand and covariates. For regressands, we use per capita expenditure for (1) - (3), total expenditure for (4) - (6). (1), (4) are OLS with no covariates, (2), (5) are OLS with covariates. (3), (6) are dummy entries used only to compute mean and standard deviation.

```{r consumption OLS regression set parameters original HHs}
source(paste0(pathprogram, "ReadTrimConsumptionANCOVA.R"))
# Page 6 of rd 4 questionnaire.
FileName <- "ConsumptionOLS"
regsuffixes <- c("", "a", "P", "T", "Ta", "TP", "TPa")
listheader <- paste0("co", regsuffixes)
exclheader <- paste0("excl", regsuffixes)
inclheader <- gsub("ex", "in", exclheader)
source(paste0(pathprogram, "ConsumptionCovariateSelectionOLS.R"))
#### jay: number of reg specs. This defines table dimension.
jay <- max(as.numeric(gsub("incl", "", ls(pattern = "^incl\\d"))))
Regressands <- c(rep("PCExpenditure", 3), rep("TotalExpenditure", 3),
  "PCExpenditure")
DataToUse1 <- DataToUse2 <- rep("conOLS", 7)
Addseparatingcols = c(1, 4); Separatingcolwidth = rep(.2, 2)
Separatingcoltitle = c("", "Per capita consumption (Tk)", 
  "Total consumption (Tk)")
dig.depmean <- 0
AddMeanStdColumn <- T
UseRawDataForDestat <- F
source(paste0(pathprogram, "ANCOVAEstimationFile3.R"))
```

<details><summary>Click here to see the table of OLS time varying consumption impacts by arm.</summary>
`r HTML_ConsumptionOLSTimeVarying`
</details>


