```{r ReadTrimConsumption OLS, echo = F, cache = F, warning = F}
source(paste0(pathprogram, "ReadTrimConsumptionANCOVA.R"))
```

Consumption is observed in rd 2-4. There are `r nrow(con)` observations. As we lack the initial value, we use OLS using rd 2- 4 values to measure the impacts. It should be less precise but still gives consistent estimates.  

Regression specifications differ in terms of regressand and covariates. For regressands, we use per capita expenditure for (1) - (2), total expenditure for (3) - (4). (1), (3) are OLS with no covariates, (2), (4) are OLS with covariates. (5) is a dummy entry used only to compute mean and standard deviation.

<details><summary>Click here to see the code of consumption impacts OLS estimation.</summary>
```{r consumption OLS regression set parameters original HHs}
source(paste0(pathprogram, "ReadTrimConsumptionANCOVA.R"))
# Page 6 of rd 4 questionnaire.
FileName <- "ConsumptionOLS"
regsuffixes <- c("", "a", "P", "T", "Ta", "TP", "TPa")
listheader <- paste0("co", regsuffixes)
exclheader <- paste0("excl", regsuffixes)
inclheader <- gsub("ex", "in", exclheader)
source(paste0(pathprogram, "ConsumptionCovariateSelectionOLS.R"))
#### jay: number of reg specs. This defines table dimension.
jay <- max(as.numeric(gsub("incl", "", ls(pattern = "^incl\\d"))))
Regressands <- c(rep("PCExpenditure", 3), rep("TotalExpenditure", 3),
  "PCExpenditure")
DataToUse1 <- DataToUse2 <- rep("conOLS", 7)
Addseparatingcols = NULL; Separatingcolwidth = NULL
Separatingcoltitle = c("", "Per capita consumption (Tk)", 
  "Total consumption (Tk)")
dig.depmean <- 0
AddMeanStdColumn <- T
UseRawDataForDestat <- F
source(paste0(pathprogram, "ANCOVAEstimationFile3.R"))
```
</details>

<details><summary>Click here to see the table of OLS time varying consumption impacts by arm.</summary>
`r HTML_ConsumptionOLSTimeVarying`
</details>


