In `ReadTrimLivestockByExperienceANCOVA.R`:  

* Net assets data + livestock data (livestock experience, ownership, and other covariates) &rArr; `lvoE` data. We use this to estimated cattle holding impacts, and impacts by experience in the later subsection.  
* Open [ReadTrimLivestockByExperienceANCOVA.R](../program/ReadTrimLivestockByExperienceANCOVA.R) to see the code.  

```{r ReadTrim NumCows, cache = F, warning = F}
source(paste0(pathprogram, "ReadTrimLivestockByExperienceANCOVA.R"))
lvoEN = copy(lvoE)
```

```{r Numcows set parameters original HHs}
FileName <- "NumCows"
FileNameHeader <- c("", "PovertyStatus", "Attributes",
  "TimeVarying", "TimeVaryingAttributes",
  "TimeVaryingPovertyStatus", "TimeVaryingPovertyStatusAttributes")
regsuffixes <- c("", "P", "a", "T", "Ta", "TP", "TPa")
listheader <- paste0("nae", regsuffixes)
source(paste0(pathprogram, "NumCowsCovariateSelectionANCOVA2.R"))
jay <- max(as.numeric(gsub("incl", "", ls(pattern = "^incl\\d"))))
DataToUse1 <- DataToUse2 <- rep("lvoEN", 7)
Addseparatingcols <- NULL; Separatingcolwidth <- NULL
Separatingcoltitle <- NULL
Regressands <- rep("NumCows", jay)
tableboxwidth <- 4.5
exclheader <- paste0("excl", regsuffixes)
inclheader <- gsub("ex", "in", exclheader)
#### source(paste0(pathprogram, "DisplayCovariates.R"))
dig.depmean <- 2
AddMeanStdColumn <- UseRawDataForDestat <- T
source(paste0(pathprogram, "ANCOVAEstimationFile3.R"))
```

<details><summary>Click here to see the results table on net non-livestock assets..</summary>
<div class="row">
  <div class="col-sm-9"> `r HTML_NumCowsTimeVarying` </div>
</div>
</details>


